Patients with Left Hemispheric Intracerebral Hemorrhage are Less Likely to Receive Neurosurgical Intervention

### 2024-06-26 manuscripts/manuscript1_supplement.qmd
updated neurosurgery manuscripts

# load data and models
with_dir(here(), tar_load(ich_aggressive))
with_dir(here(), tar_load(dag_aggressive))
with_dir(here(), tar_load(m_prior_default_neurosurgery))
with_dir(here(), tar_load(m_prior_informative_neurosurgery))

@@

m_prior_informative_neurosurgery

@@

```{r informative prior predictive check - neurosurgical intervention}
#| echo: false
#| fig-height: 12

avg_predictions(m_prior_informative_neurosurgery, variables = "ich_laterality")

ggplot(mutate(spread_draws(m_prior_informative_neurosurgery, b_ich_lateralityRight),
  ich_right_or = exp(b_ich_lateralityRight)
), aes(ich_right_or)) +
  geom_density(color = "#422f05", fill = "#E69F00") +
  scale_x_continuous(breaks = seq(-10, 10, 0.25)) +
  labs(
    title = "Odds Ratio - Right Hemisphere",
    y = NULL, fill = NULL
  ) +
  geom_vline(
    xintercept = 1, linetype = "dashed",
    color = "#999999", linewidth = 1
  ) +
  theme_ich() +
  theme(legend.position = "none")

>>>>

# load data and models
with_dir(here(), tar_load(ich_aggressive))

@@

@@

```{r informative prior predictive check - neurosurgical intervention}
#| echo: false
#| fig-height: 12
#|

with_dir(here(), tar_load(m_prior_neutral_neurosurgery))
with_dir(here(), tar_load(m_prior_left_neurosurgery))

avg_predictions(m_prior_left_neurosurgery, variables = "ich_laterality")

results_visual(m_prior_left_neurosurgery, "Prior Predictive Check")
